Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-02-07 paper.tex
saque la oracion de 6 triangulos por nodo

It is worth noting from Fig.~\ref{degree_dens} that ``stiff''
pedestrians exhibit a sharper transition to the maximum packing density than 
the ``soft'' pedestrians. We further checked this phenomenon by counting the 
number of loops of three nodes (say, the triangles) present in the network. 
This magnitude was reported to be a sensitive magnitude for characterizing the 
jamming transition in a compressed granular packing (see 
Ref.~\cite{pugnaloni_2013} for details).  As can be seen in 
Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
than the ``soft'' ones.\textcolor{red}{ The maximum number of allowed triangles is 6, 
corresponding to a hexagonal arrangement.}    \\

>>>>

It is worth noting from Fig.~\ref{degree_dens} that ``stiff''
pedestrians exhibit a sharper transition to the maximum packing density than 
the ``soft'' pedestrians. We further checked this phenomenon by counting the 
number of loops of three nodes (say, the triangles) present in the network. 
This magnitude was reported to be a sensitive magnitude for characterizing the 
jamming transition in a compressed granular packing (see 
Ref.~\cite{pugnaloni_2013} for details).  As can be seen in 
Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
than the ``soft'' ones.   \\
